\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
JRC logo added, some other small modifications
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64803 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, $^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Itlay}

@@

\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
%Please insert your institution logo here
\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
\addlogo[north east]{(-2,-5.5)}{4cm}{svg_images/NC_State_Seal.pdf}
\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}{
\small \noindent Geographical Information Systems (GIS) is known for its capacity to spatially enhance the capacity of man- agement of natural resources. While being often used as an analytical tool, it also represents a collaborative scientific platform to develop new algorithms. GRASS GIS \cite{neteler2012grass}, a free and open source GIS, is used by many scientists directly or through other projects such as R or QGIS to perform geoprocessing tasks. Thus, a large number of scientific geospatial computations depend on quality and correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility of scientific results over time as the original author designed it \cite{rocchini2012let}. Moreover, subsequent improvements are tracked in the source code versioning system and are immediately available to the public (Petras, 2014). Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline

@@

A set of modules for multiscale analysis of landscape structure was added in 1992 by \cite{baker1992r} who developed the r.le model similar to FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually improved to become r.li in 2006. Further development continued, with a significant speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years ago, since then it was improved several times (Trac2, 2014). It is an important part of GRASS GIS and is even taught at geospatial modeling courses, for example http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline

@@

The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS functions r.ros and r.spread, is object of active research. It has been exten- sively tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; \cite{derigo2013architecture} ; Di Leo et al., 2013).

@@

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./svg_images/public_domain_logo.pdf}
\end{minipage}

>>>>

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, 
\\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
$^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Italy}

@@

\addlogo[north west]{(2,-1)}{9cm}{images/Grass_GIS}
%Please insert your institution logo here
\addlogo[north east]{(-2,-2.5)}{4cm}{images/logo_FEM_CRI}
\addlogo[north east]{(-2,-5.5)}{4cm}{images/NC_State_Seal}
\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut}
\addlogo[north east]{(-8,-6.5)}{4cm}{images/IWMI_logo}
\addlogo[north east]{(-2,-10.5)}{4cm}{images/logo_ec-jrc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}
{
\small \noindent Geographical Information Systems (GIS) is known for its capacity 
to spatially enhance the capacity of man- agement of natural resources. 
While being often used as an analytical tool, it also represents a collaborative 
scientific platform to develop new algorithms. GRASS GIS \cite{neteler2012grass}, 
a free and open source GIS, is used by many scientists directly or through other 
projects such as R or QGIS to perform geoprocessing tasks. Thus, a large number 
of scientific geospatial computations depend on quality and correct functionality 
of GRASS GIS. Integrating scientific algorithms into GRASS GIS helps to preserve 
reproducibility of scientific results over time as the original author designed 
it \cite{rocchini2012let}. Moreover, subsequent improvements are tracked in the 
source code versioning system and are immediately available to the public (Petras, 2014). 
Thus, GRASS GIS acts as a repository of scientific peer-reviewed code and 
algorithm/knowledge hub for future generation of scientists.\vspace{5mm}\newline

@@

A set of modules for multiscale analysis of landscape structure was added in 1992 
by \cite{baker1992r} who developed the r.le model similar to 
FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
improved to become r.li in 2006. Further development continued, with a significant 
speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline

@@

The wildfire simulation toolset, firstly developed by \cite{xu1994simulating}, 
implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
functions r.ros and r.spread, is object of active research. It has been extensively 
tested and recently adapted to European fuel types (\cite{rodriguez2013data} ; 
\cite{derigo2013architecture} ; Di Leo et al., 2013).
}

@@

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/public_domain_logo}
\end{minipage}
